---
title: "Case01_Brewery"
author: "Andrew Shen"
date: "June 27, 2017"
output: html_document
---

# R Markdown
## R Markdown
### R Markdown
#### R Markdown
##### R Markdown
###### R Markdown

#Introduction:
###This Case study ties 2 data sets together about breweries and the beer they make. 
###From the brewery & beer merged data,we look at the bitterness and alcohol by vloume (ABV) in relation to their brewwery state. 
###We then will look further into the relationship between betterness and ABV and see if there is a correlation.

##Importing the Raw Data d

```{r}
setwd("C:/Users/Drew/Documents/R/Doing Data Science/Breweries/Case-Study-01-Beer")

beers<- read.csv("C:\\Users\\Drew\\Desktop\\Doing Data Science MSDS 6306\\Case File\\Beers.csv")
breweries<- read.csv("C:\\Users\\Drew\\Desktop\\Doing Data Science MSDS 6306\\Case File\\Breweries.csv")

#   packages used    
library(tidyverse)
library(plyr)
#  Questions    

#1 How many Breweries are present in each state?

count(breweries,'State')
```
#2 Merge beer data with breweries data by brewery id. Print first 6 observations and the 
#last six observations to check the merged file. 

#merging data
```{r}
colnames(beers)
colnames(breweries)
colnames(beers)[colnames(beers)=="Brewery_id"] <- "Brew_ID"
colnames(beers)

master_beer <- merge(breweries,beers,by="Brew_ID")
str(master_beer)
#First 6 obs master_beer
head(master_beer, n=6)

#3  Report the number of NA's in each column. 

colSums(is.na(master_beer))

#4 Compute the median alcohol content and international bitterness unit for each state. Plot
#a bar chart to compare. 

med.abv<-tapply(master_beer$ABV, master_beer$State, median)
med.IBU<-tapply(master_beer$IBU, master_beer$State, median)

barplot(med.abv)
barplot(med.IBU)

#5 Which state has the maximum alcoholic beer? Which state has the most bitter beer? 
master_beer[which.max(master_beer$ABV),]
master_beer[which.max(master_beer$IBU),]

#6 Summary statistics for ABV (Alcohol by volume) variable. 
summary(master_beer$ABV)

#7 Is there a relationship between the bitterness of the beer and its alcoholic content? Draw
#a scatter plot. 
ggplot(data = master_beer, mapping = aes(x = master_beer$ABV, y = master_beer$IBU))+
  geom_point() +
  geom_smooth(method = lm) 

cor.test(master_beer$ABV,master_beer$IBU)
myfit <- lm(master_beer$ABV ~ master_beer$IBU, data=master_beer)

summary(myfit)
confint(myfit)

